%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Self-Learning Project | Flutter} % Job title
    {Chat App} % Organisation
    {Roorkee, India} % Location
    {Dec 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Currently making a chat app with proper authentication with the UI inspired by Instagram.}
        \item {Made chatrooms where an user can search for another user and text him.}
        \item {GitHub link: {\href{https://github.com/anshikamittal25/instagram_clone}{\bf Chat App}}.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\cventry
    {Self-Learning Project | Flutter} % Job title
    {Entry Register} % Organisation
    {IIT Roorkee} % Location
    {November 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {It eases the process of writing and managing entries for both the residents and the administration of the hostel respectively.}
        \item {Used Android Studio as a development tool and Cloud Firestore for data storage and Firebase Auth for authentication}
        \item {Set up the navigation and structured code in a modular way and used Future Builder, Shared Preferences,etc.}
        \item {GitHub link: {\href{https://github.com/anshikamittal25/entry_register}{\bf Entry Register}}.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\cventry
    {Self-Learning Project | Flutter} % Job title
    {World Time App} % Organisation
    {IIT Roorkee} % Location
    {Oct 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {It shows the time of different countries along with their flags.}
        \item{Changes the background depending on whether it is day or night in the country.}
        \item {Made http request to world time API for data and structured code in a modular way.}
        \item {GitHub link: {\href{https://github.com/anshikamittal25/world_time}{\bf World Time App}}.}
      \end{cvitems}
    }
      

%---------------------------------------------------------
\cventry
    {Web Developer} % Job title
    {Color Game} % Organisation
    {IIT Roorkee} % Location
    {Feb 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created RGB color game using HTML, CSS and JavaScript.}
        \item{Helps the user to get an idea of RGB color formats while playing in 2 different levels- easy and hard.}
        \item {Used event listeners and generated different colors to choose from using random function.}
        \item {Github link: \href{https://github.com/anshikamittal25/color_game}{\bf Color Game}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
